---
title: "Spotify Streaming History"
author: "Anthony Tetreault"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DBI)
library(RPostgreSQL)
library(tidyverse)

get_pword <- function() {
    pword <- readline("Enter password: ")
    return(pword)
}

conn <- dbConnect(RPostgreSQL::PostgreSQL(),dbname = 'Spotify', 
                 host = 'localhost',
                 port = 5432,
                 user = 'tetreault',
                 password = get_pword())
```

## Spotify Extended Streaming History

#### 1. Count plays per artist per year
```{r}
query1 <-   'select
            	artist_name,
            	count(*) as plays,
            	extract(year from timestamp) as year
            from
            	streaming_history
            where
            	time_played > 120 and 
            	artist_name is not null
            group by
            	extract(year from timestamp),
            	artist_name
            order by
            	extract(year from timestamp) desc,
            	count(*) desc;'
artist_plays_byyr <- as_tibble(dbGetQuery(conn, query1))
artist_plays_byyr1 <- artist_plays_byyr %>% 
    group_by(year) %>% slice(1:10)
artist_plays_byyr1
ggplot(artist_plays_byyr1, aes(artist_name, plays)) +
    geom_col() +
    facet_wrap(~ year)
```

#### 2. Count plays per episode per year 
```{r}
query2 <-   'select
            	episode_show_name,
        	    count(*) as plays,
        	    extract(year from timestamp) as year
            from
        	    streaming_history
            where
        	    time_played > 120 and
        	    episode_show_name is not null
            group by
        	    extract(year from timestamp),
        	    episode_show_name
            order by
        	    extract(year from timestamp) desc,
        	    count(*) desc;'

podcast_plays_byyr<- tibble(dbGetQuery(conn, query2))
podcast_plays_byyr
```

#### 3. Sum time played per artist per year
```{r}
query3 <- 'select
            	artist_name,
            	sum(time_played) as tot_time_played,
            	extract(year from timestamp) as year
            from
            	streaming_history
            where
            	artist_name is not null and
            	time_played > 120
            group by
            	extract(year from timestamp),
            	artist_name
            order by
            	extract(year from timestamp) desc,
            	sum(time_played) desc;'
artist_time_byyr<- tibble(dbGetQuery(conn, query3))
```

#### 4. Most played artist (all time) -- BY count or time?
```{r}
query4 <-   'select
            	plays,
            	tot_time_played,
            	artist_name
            from 
            	(select
            		count(*) as plays,
            		sum(time_played) as tot_time_played,
            		artist_name
            	from
            		streaming_history
            	where
            		time_played > 120 and
            		artist_name is not null
            	group by
            		artist_name)
            order by
            	plays desc,
            	tot_time_played desc;'

mp_artist_at<- tibble(dbGetQuery(conn, query4))
```

#### 5. Most played song (all time) -- by count or time?
```{r}
query5 <- ''

mp_track_at <- tibble(dbGetQuery(conn, query5))
```

#### 6. Most played album (all time) (by count)
```{r}
query6 <-   'select
            	sh.artist_name,
            	albums.album_name,
            	albums.plays
            from
            	(select
            		album_name,
            		count(*) as plays
            	from 
            		streaming_history
            	where
            		time_played > 120 and
            		artist_name is not null
            	group by
            		album_name) as albums
            left join streaming_history sh 
            	on sh.album_name = albums.album_name
            group by
            	albums.album_name,
            	sh.artist_name,
            	albums.plays
            order by 
            	albums.plays desc;'

mp_album_at <- tibble(dbGetQuery(conn, query6))
```

#### 7. Most played podcast (all time) (by time_played)
```{r}
query7 <-   'select
            	episode_show_name,
            	sum(time_played) as tot_time_played
            from
            	streaming_history
            where 
            	episode_show_name is not null and
            	time_played > 120
            group by
            	episode_show_name
            order by
            	sum(time_played) desc;'

mp_pod_at <- tibble(dbGetQuery(conn, query7))
```

#### 8. Most played artist (by year) -- by count or time?
```{r}
# Most listened to artist per year by time played
query8 <-   'select 
            	extract(year from timestamp) 		as year,
            	round(sum(time_played)::numeric, 2) as total_time_played,
            	artist_name
            from
            	streaming_history sh
            where
            	time_played > 120 and
            	artist_name is not null
            group by
            	extract(year from timestamp),
            	artist_name
            order by
            	extract(year from timestamp) desc,
            	sum(time_played) desc;'
mp_artist_byyr <- tibble(dbGetQuery(conn, query8))
mp_artist_byyr1 <- mp_artist_yr 
    
```

#### 9. Most played song (by year) -- by count or time?
```{r}
query9 <- ''

mp_track_byyr <- tibble(dbGetQuery(conn, query9))
```

#### 10. Most played album (by year) (by count)
```{r}
query10 <-  'select
            	extract(year from timestamp) as year,
            	count(*) as plays,
            	album_name,
            	artist_name
            from
            	streaming_history
            where
            	album_name is not null and
            	(skipped is false or time_played > 60)
            group by
            	extract(year from timestamp),
            	album_name,
            	artist_name
            order by
            	extract(year from timestamp) desc,
            	count(*) desc;'

mp_album_byyr <- tibble(dbGetQuery(conn, query10))
```

#### 11. Most played podcast (by year) (by time_played)
```{r}
query11 <- 'select
            	extract(year from sh.timestamp) as year,
            	episode_show_name,
            	round(sum(time_played)::numeric, 2) as total_time_played
            from 
            	streaming_history sh
            where
            	time_played > 1 and
            	episode_show_name is not null
            group by
            	extract(year from sh.timestamp),
            	episode_show_name
            order by
            	extract(year from sh.timestamp) desc,
            	sum(time_played) desc;'
mp_pod_yrly <- tibble(dbGetQuery(conn, query11))
mp_pod_yrly1 <- mp_pod_yrly %>% 
    filter()

```

#### 12. Most skipped artist
```{r}
query12 <-  'select
            	artist_name,
            	count(*) as skips
            from
            	streaming_history
            where
            	skipped is true and
            	artist_name is not null
            group by
            	artist_name
            order by
            	count(*) desc;'
most_skipped_artist <- tibble(dbGetQuery(conn, query12))
```

#### 13. Most skipped track
```{r}
query13 <- 'select
                track_name,
                artist_name,
                count(*) as skips
            from
                streaming_history
            where
                skipped is true and
                artist_name is not null
            group by
                track_name,
                artist_name
            order by
                count(*) desc;'
most_skipped_track <- tibble(dbGetQuery(conn, query13))
```

#### 14. Time of day habits -- by hour or noun quarters? or both?
```{r}
query14 <- "select
            	extract('hour' from timestamp) as hour,
            	sum(time_played) as tot_time_played
            from
            	streaming_history
            group by
            	extract('hour' from timestamp)
            order by
            	hour;"

time_of_day <- tibble(dbGetQuery(conn, query))
time_of_day1 <- time_of_day %>% 
    mutate(tot_time_played = tot_time_played / 60)
tod_plot <- ggplot(time_of_day1, mapping = aes(hour, tot_time_played)) +
    geom_col() +
    
tod_plot

```

